---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-"
)
```

# rstatix

Provides a pipe-friendly framework to perform easily basic statistical tests in R. The output of each test is automatically transformed into a tidy data frame to facilitate visualization.
   
Main functions include:
  
- `t_test()`: performs one-sample, two-sample and pairwise t-tests
- `wilcox_test()`: performs one-sample, two-sample and pairwise Wilcoxon tests
- `adjust_pvalue()`: add an adjusted p-values column to a data frame containing statistical test p-values
- `add_significance()`: add a column containing the p-value significance level
   
   
## Installation and loading
    
    
- Install the latest version from [GitHub](https://github.com/kassambara/rstatix) as follow: 
    
   
```{r, eval = FALSE}
# Install
if(!require(devtools)) install.packages("devtools")
devtools::install_github("kassambara/rstatix")
```
     
     
- Loading packages
   
```{r}
library(rstatix)  
library(ggpubr)  
```

     
## Comparing means
   
   
### Comparing two groups
   
   
- Two sample t-test
   
```{r two-sample-t-test, fig.width=3, fig.height=3}
ToothGrowth %>% 
  t_test(len ~ supp, paired = FALSE)

ToothGrowth %>%  ggboxplot(
  x = "supp", y = "len",
  color = "supp", palette = "jco"
  )
```


- Compare supp levels after grouping the data by "dose"
   
```{r -grouped-two-sample-t-test, fig.width=6, fig.height=3}
# Statistical test
ToothGrowth %>%
  group_by(dose) %>%
  do(t_test(data =., len ~ supp)) %>%
  ungroup() %>%
  adjust_pvalue() %>%
  add_significance("p.adj")

# Visualization
ggboxplot(
  ToothGrowth, x = "supp", y = "len",
  color = "supp", palette = "jco",facet.by = "dose"
  ) +
  stat_compare_means(method = "t.test")
```
   
   
- Pairwise comparisons
   
   
```{r}
# pairwise comparisons
#::::::::::::::::::::::::::::::::::::::::
# As dose contains more thant two levels ==>
# pairwise test is automatically performed.
ToothGrowth %>% t_test(len ~ dose)

# Comparison against reference group
#::::::::::::::::::::::::::::::::::::::::
# each level is compared to the ref group
ToothGrowth %>% t_test(len ~ dose, ref.group = "0.5")

# Comparison against all
#::::::::::::::::::::::::::::::::::::::::
ToothGrowth %>% t_test(len ~ dose, ref.group = "all")
```

